Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-28 cav2017/cav2017.tex
authors
edits

%\toctitle{Lecture Notes in Computer Science}
%\tocauthor{Authors' Instructions}
\author{Anonymous}
\institute{}

@@

We are not limited to the synthesis of digital stabilizing controllers -- a
well known task in the literature on digital control system -- but target
safety requirements with an overall approach that is sound and automated. 
More specifically, we require that the closed-loop system
\eqref{eq:closedloopss} meets given safety specifications.  A safety
specification raises a requirement on the states of the model, such that the
feedback controller (namely the choice of the gains matrix~$K$) must ensure
that the states never exit such requirement.  Note that a stable,
closed-loop system is not necessarily a safe system: indeed, the state
values may leave the safe space whilst they converge to the equilibrium,
which is typical in the case of oscillatory dynamics.  However, a safe
system will always be stable.  In~this work, the safety property represented
by $\phi_\mathit{safety}$ is encoded as follows:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_\mathit{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
instant, respectively.  This means that the states will always be within the
$n$-dimensional hyper-box.

>>>>

%\toctitle{Lecture Notes in Computer Science}
%\tocauthor{Authors' Instructions}

\author{%
Alessandro Abate \and
Iury Bessa \and
Dario Cattaruzza \and
Lucas Cordeiro \and
\mbox{Cristina David} \and
Pascal Kesseli \and
Daniel Kroening \and
Elizabeth Polgreen}

\institute{}

@@

We are not limited to the synthesis of digital stabilizing controllers -- a
well known task in the literature on digital control system -- but target
safety requirements with an overall approach that is sound and automated. 
More specifically, we require that the closed-loop system
\eqref{eq:closedloopss} meets given safety specifications.  A safety
specification raises a requirement on the states of the model, such that the
feedback controller (namely the choice of the gains matrix~$K$) must ensure
that the states never exit such requirement.  Note that a stable,
closed-loop system is not necessarily a safe system: indeed, the state
values may leave the safe space whilst they converge to the equilibrium,
which is typical in the case of oscillatory dynamics.  However, a safe
system will always be stable.  In~this work, the safety property 
is modeled as follows:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
instant, respectively.  This means that the states will always be within the
$n$-dimensional hyper-box.
